\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Niki Vazou} \\ \vspace{1pt}
    \small \href{mailto:niki.vazou@imdea.org}{\underline{niki.vazou@imdea.org}} $|$ 
    \href{https://nikivazou.github.io/}{\underline{nikivazou.github.io}} $|$
    \href{https://scholar.google.com/citations?user=ARcLTokAAAAJ&hl=en}{\underline{scholar.google}} $|$
    \href{https://github.com/nikivazou}{\underline{github.com/nikivazou}} % $|$
%    \href{https://twitter.com/nikivazou}{\underline{twitter.com/nikivazou}}
\end{center}


%-----------POSITIONS-----------
\section{Positions}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Research Associate Professor}{2022 – present}
  {IMDEA Software Institute, Madrid, Spain.}{}
  \resumeSubheading
    {Research Assistant Professor}{2018 – 2022}
    {IMDEA Software Institute, Madrid, Spain.}{}
    \resumeSubheading
    {Postdoctoral Fellow}{2017 - 2018}
    {Computer Science Department, University of Maryland, College Park, USA.}{}

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Phd}{2011-2017}
      {Computer Science and Engineering, University of California, San Diego, USA.}{}

      {Supervisor: Ranjit Jhala; Thesis title: “Liquid Haskell: Haskell as a Theorem Prover”.}{}
    \resumeSubheading
      {Diploma}{2005-2010}
      {National Technical University of Athens, Athens, Greece.}{}

      {Supervisor: Nikolaos Papaspyrou; Thesis title: “Memory Safety with Linear Capabilities”.}{}
  \resumeSubHeadingListEnd

% \begin{comment}  
\section{(Co-)Supervision of Graduate Students \& Interns}
\resumeSubHeadingListStart
\resumeProjectHeading
    {IMDEA Software Institute, Madrid, Spain.}{Present}
    \resumeItemListStart
      \resumeItem{PhD candidate Lisa Vasilenko on “Relational refinement types”.}
      \resumeItem{PhD candidate Antonio Zegarelli on “Dynamic Policies”.}
      \resumeItem{PhD candidate Colin Rothgang on “Refinement to Dependent Types”.}
    \resumeItemListEnd

\resumeProjectHeading
    {}{Past}
    \resumeItemListStart
    \resumeItem{Research intern Zack Grannan on “Rewriting for Liquid Haskell”. \emph{Published at ECOOP'23.}}
    \resumeItem{PhD candidate Milod Kazerounian on “Refinement types for Ruby”. \emph{Published at VMCAI'18 and PLDI'19.}}
    \resumeItem{PhD candidate James Parker on “Verification of secure web applications”. \emph{Published at POPL'19 and OOPSLA'20.}}
    \resumeItemListEnd

\resumeProjectHeading
    {National Technical University of Athens, Athens, Greece.}{2018}
    \resumeItemListStart
    \resumeItem{Diploma student George Petrou on “Verification with Liquid Haskell”.}
    \resumeItemListEnd
\resumeSubHeadingListEnd



\section{Teaching Activities}
\resumeSubHeadingListStart

\resumeSubheading
  {Computer Science Department, Universidad Politecnica de Madrid, Madrid, Spain.}{Fall 2019}
  {2 months/20 hours seminar on Advanced Functional Programming.}{}
\resumeSubheading
  {Computer Science Department, University of Maryland, College Park, USA.}{Winter 2018}
  {Lecturer at Advanced Functional Programming (CMSC498V).}{}
\resumeSubheading
  {Computer Science Department, University of Maryland, College Park, USA.}{Fall 2017}
  {Co-Lecturer at Introduction to Programming (CMSC330).}{}
\resumeSubheading
  {Clubes De Ciencia, Guanajuato, Mexico.}{Summer 2015}
  {1 week/40 hours course on Functional Programming.}{}
  
\resumeSubHeadingListEnd
%\end{comment}

\section{Reviewing Activities}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{ ESOP'25, PLDI'24, TyDe'24 ICFP'23, PLDI'23, ESOP'23, HaskellX'22, POPL’22, WITS'22, TYPES'22, OOPSLA'22, FLOPS'22, PLS'21, PEPM'21, VMCAI’21, WGT'20, CAV’20, FCS’20, POPL’19, ESOP’18, ICFP’18, PEPM’21, PLS’21, TFP’20, Haskell’18, ML-Family Workshop’17, HOPE’17, PADL’17, Scala’17, Haskell’16, HiW’16, TFP’16, PADL’16, Scala’16, AEC@POPL’16, AEC@PLDI’16.
    }}
 \end{itemize}

%\begin{comment}
 \section{Invited Talks}
 \resumeSubHeadingListStart
 \resumeProjectHeading
 {Invited at PLMW at POPL}{2024}
 \resumeProjectHeading
 {Keynote at LFMTP: Logical Frameworks and Meta-Languages: Theory and Practice}{2023}
 \resumeProjectHeading
 {Presenter at SCOT Seminar}{2022}
 \resumeProjectHeading
 {Keynote at CLAS: Computational Logic Autumn Summit}{2022}
 \resumeSubHeadingListEnd


 \section{Organization of Scientific Events}
\resumeSubHeadingListStart
\resumeProjectHeading
    {Co-Chair, Sponsoring PLDI.}{2024}
\resumeProjectHeading
    {Co-Chair, Haskell Symposium.}{2024}
\resumeProjectHeading
    {Co-Chair, Haskell Symposium.}{2023}
\resumeProjectHeading
    {Co-Chair, Artifact Evaluation, PLDI.}{2022}
\resumeProjectHeading
    {Co-Chair, Artifact Evaluation, PLDI.}{2021}
\resumeProjectHeading
    {Virtualization Committee, ICFP.}{2020}
\resumeProjectHeading
    {Co-Chair, Student Research Competition, POPL.}{2020}
\resumeProjectHeading
    {Chair, Student Research Competition, POPL.}{2019}
\resumeProjectHeading
    {Chair, Haskell Implementors’ Workshop.}{2019}
\resumeProjectHeading
    {Co-Chair, Programming Languages and Analysis for Security.}{2019}
\resumeProjectHeading
    {Co-Organizer, Programming Languages Mentoring Workshop, ICFP.}{2018}
\resumeProjectHeading
    {Co-Chair, Workshop on Type-Driven Development.}{2018}
\resumeSubHeadingListEnd

%\end{comment}
\section{Membership of Scientific Societies}
\resumeSubHeadingListStart
\resumeProjectHeading
    {Member of SIGPLAN Executive Committee.}{2024 - present}
    \resumeProjectHeading
    {Member of IFIP Working Group 2.1 on Algorithmic Languages and Calculi.}{2024 - present}
\resumeProjectHeading
    {Member of IFIP Working Group 2.8 on Functional Programming.}{2024 - present}
\resumeProjectHeading
    {Member of The ACM SIGPLAN Haskell Symposium Steering Committee.}{2023 - present}
\resumeProjectHeading
    {Member of the Dahl-Nygaard Prize Committee.}{2023}
\resumeProjectHeading
    {Board Member of Haskell Foundation.}{2021 - 2022}
\resumeProjectHeading
    {Member of Haskell.org Committee.}{2016 - 2020}
\resumeProjectHeading
    {Event Coordinator at Graduate Women in Computing, UCSD.}{2015 - 2016}
\resumeSubHeadingListEnd




 \section{Grants \& Awards}
 \resumeSubHeadingListStart
 \resumeProjectHeading
     {ERC Starting Grant}{2022-2027}
 \resumeProjectHeading
     {Wallenberg Academy Fellowship.}{2021}
 \resumeProjectHeading
     {Juan de la Cierva Incorporacion Grant, by Spanish Ministry of Science and Innovation.}{2021 - 2023}
 \resumeProjectHeading
     {Atraccion de Talento Fellowship, by Madrid Regional Government.}{2020 - 2024}
 \resumeProjectHeading
     {Best paper award at ACM SIGPLAN Conference OOPSLA.}{2018}
 \resumeProjectHeading
     {Victor Balisi Postdoctoral Fellowship, University of Maryland, College Park, USA.}{2017 - 2018}
 \resumeProjectHeading
     {Graduate Award for Research, University of California, San Diego, USA.}{2015}
 \resumeProjectHeading
     {Microsoft Research Graduate Research Fellowship.}{2014 - 2016}
 \resumeSubHeadingListEnd
 
 \vspace*{\fill}
 \hfill \emph{Last Updated: July 2024}
%-------------------------------------------
\end{document}